---
title: "Burkina Faso data using EpiCyst Model"
date: "27.04.2021"
---
```{r, include=FALSE}
rm(list = ls())
Sys.setenv(LANG = "en")
setwd("C:/Users/morika/Desktop/AdvOneHealth/")

library(epicyst)
library(ggplot2)
library(dampack)
library(kableExtra)
library(dplyr)
library(googlesheets4)
```

```{r eval=FALSE, include=FALSE}
url <- "https://docs.google.com/spreadsheets/d/1wovS9EKz_yV6kTNZ6td8rUvGUHTQjDkJNlrHrKVJtOE/edit#gid=1862836567"
urlh <- "https://docs.google.com/spreadsheets/d/1fFyn-5kfc4PD9oVc_E6zCod7GwJVF-POYLJXygIt1UU/edit#gid=1862836567"

read_sheet(url)
ssid <- as_sheets_id(url)
unclass(ssid)

read_sheet(urlh)
ssid <- as_sheets_id(urlh)
unclass(ssid)

gs4_auth(
email = "kathleenbmoriarty@gmail.com",
path = NULL,
scopes = "https://www.googleapis.com/auth/drive",
cache = "path_to_cache",
use_oob = FALSE,
token = NULL)

#gs_auth(new_user = TRUE)
```
## Import Data from Google Sheets

```{r, message=FALSE, warning=FALSE}


ssid <- "1wovS9EKz_yV6kTNZ6td8rUvGUHTQjDkJNlrHrKVJtOE"
ssidh <-"1fFyn-5kfc4PD9oVc_E6zCod7GwJVF-POYLJXygIt1UU"
costs <- read_sheet(ssid, sheet = "SSA_Costs_V2")
costsh <- read_sheet(ssidh, sheet = "SSA_Costs_V2")

#dalys <- read_sheet(ssid, sheet = "SSA_DALYs", range = "A2:B7")
cparams <- read_sheet(ssid, sheet = "BF_Params")

```

## Initial setup

```{r}

#Create Burkina Faso subset
aparams <- set_up(PPS=cparams[which(cparams$Param=="PPS"),]$Val, 
                   HPS = cparams[which(cparams$Param=="HPS"),]$Val,
                   TPrev = cparams[which(cparams$Param=="TPrev"),]$Val, 
                   CPrev = cparams[which(cparams$Param=="CPrev"),]$Val, 
                   LEH=cparams[which(cparams$Param=="LEH"),]$Val, 
                   LEP=cparams[which(cparams$Param=="LEP"),]$Val)

#Parameters
#aparams[[1]]$HPS

#State variables
#aparams[[2]]

```

## Run model with Baseline and Interventions
* time: months
* steps: per unit of time


```{r}

dfSQ <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1)

g1 <- ggplot(data=dfSQ, aes(x=t/12, y=Humans_Cysticercosis/1000, color="Baseline"))+
  geom_line()+
  ylim(0,1000)+ 
  xlim(0,30)+
  labs(title="T. Solium Interventions in Burkina Faso",x="Time (years)", y = "Human Cysticercosis Cases (x 10^3)") +
  theme_light() +
  theme(legend.title = element_blank()) 

#Model with Sanitation intervention
dfSAN <- run_model(params=aparams[[1]], initial_states=aparams[[2]], time = 50, step = 1, intervention="Sanitation", intervention_time = 3)

#Model with Pig MDA intervention
dfPMDA <- run_model(params=aparams[[1]], initial_states=aparams[[2]], time = 50, step = 1, intervention="Pig_MDA", intervention_time = 3)

#Model with Pig Vaccination intervention
dfPVAC <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention="Pig_vaccine", intervention_time = 3)

#Model with HT&T intervention
#Updated effect_size of HT&T to assume coverage of 80% instead of 90%
#assumed therapeutic coverage (80%) × sensitivity of test to T. solium (0.97) × specificity of the test to cysticercosis infection (0.98) × assumed drug efficacy (99%) = 0.75
eff <- intervention_effect_size()
eff$Human_test_and_treat <- 0.75
dfHTT <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention="Human_test_and_treat", intervention_time = 3, intervention_effect = eff)

#Model with Pig MDA + Pig Vaccination intervention
dfPCOMBO <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention=c("Pig_MDA","Pig_vaccine"), intervention_time = 3)

#Model with Pig MDA + Pig Vaccination + HT&T intervention
dfACOMBO <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention=c("Pig_MDA","Pig_vaccine", "Human_test_and_treat"), intervention_time = 3, intervention_effect = eff)

#Model with Pig MDA + Sanitation
dfPSCOMBO <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention=c("Pig_MDA","Sanitation"), intervention_time = 3)

#Add to graph
g2<- g1 + 
  geom_line(data=dfSAN, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Sanitation")) +
  geom_line(data=dfPMDA, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA")) +
  geom_line(data=dfPVAC, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig Vaccination")) +
  geom_line(data=dfHTT, aes(x=t/12,y=Humans_Cysticercosis/1000, color="HT&T")) +
  geom_line(data=dfPCOMBO, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA + Pig Vaccination"))+
  geom_line(data=dfACOMBO, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA + Pig Vacc + HT&T")) +
  geom_line(data=dfPSCOMBO, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA + Sanitation"))
  

#Changing graph features 
g2 <- g2 + scale_colour_manual("", 
                      breaks = c("Baseline","Sanitation","Pig MDA", "Pig Vaccination", "HT&T", "Pig MDA + Pig Vaccination", "Pig MDA + Pig Vacc + HT&T", "Pig MDA + Sanitation"),
                      values = c("black", "purple", "blue","green","darkorange2","deeppink1","turquoise3", "slategrey")) +
  theme_light() +
  theme(legend.title = element_blank()) 

plot(g2)


```


## Calculate R0

```{r}
r0(params= aparams[[1]])

```

## BCR: Benefit Cost Ratio

### Assumptions:

* Cost per pig case of cysti: 14 USD
* Cost per human case of cysti: 230 USD
* Other costs explained in spreadsheets

```{r}
#Functions
prepCompare = function(df, strAcronym) {

df_short <- df[which(df$t %% 12==1 & df$t < 362),]
df_short <- df_short %>%
  mutate(t = (t-1)/12) %>% 
  select(t, Humans_Cysticercosis, Pigs_Cysticercosis, Humans_Taeniasis)

#df_short <- df_short %>% select(t, Humans_Cysticercosis, Pigs_Cysticercosis, Humans_Taeniasis)
colnames(df_short) <- c("t", paste(strAcronym,"_H_Cysti", sep=""), paste(strAcronym,"_P_Cysti", sep=""), paste(strAcronym,"_H_Tae", sep=""))

#if dfCompare is empty, then set first intervention to equal dfCompare
if (dim(dfCompare)[1] == 0) {
  print("DFCOMPARE is empty")
  dfCompare <- df_short
} else {
  print("DFCOMPARE is nOT empty")
  
   dfCompare <- merge(dfCompare, df_short, by=c("t"))
}

  return(dfCompare)
}

#calcBCR = function(dfCompare, strAcronym){
#  bcr_tmp = paste("bcr_", strAcronym, sep="")
#  p_cysti_tmp = paste(strAcronym, "_P_Cysti", sep="")
#  h_cysti_tmp = paste(strAcronym, "_H_Cysti", sep="")
#  cost_tmp = paste(strAcronym, "_Cost", sep="")
#  
#  dfCompare <- dfCompare %>% mutate(bcr_tmp = ((SQ_P_Cysti-p_cysti_tmp)*costPig + #(SQ_H_Cysti-h_cysti_tmp)*costHuman) / cost_tmp)
#  
#  return(dfCompare)
#}

#Intial values
costPig <- as.double(costs[1,"Cost_Per_Pig_Case"])
costHuman <- as.double(costs[1,"Cost_Per_Human_Case"])

tot_pop = aparams[[1]]$HPS
cost_tae = as.double(costs[1,"Costs_HTT_Taeniasis"])
cost_cysti = as.double(costs[1,"Costs_HTT_Cysti"])
costs_test = as.double(costs[1,"Costs_HTT_Test"])

dfCompare <- data.frame(t=integer())
dfCompareh <- data.frame(t=integer())

#Gather all data from the various model runs
dfCompare <- prepCompare(dfSQ, "SQ")
dfCompare <- prepCompare(dfSAN, "SAN")
dfCompare <- prepCompare(dfHTT, "HTT")
dfCompare <- prepCompare(dfPMDA, "PMDA")
dfCompare <- prepCompare(dfPVAC, "PVAC")

dfCompareh <- prepCompare(dfSQ, "SQ")
dfCompareh <- prepCompare(dfSAN, "SAN")
dfCompareh <- prepCompare(dfHTT, "HTT")
dfCompareh <- prepCompare(dfPMDA, "PMDA")
dfCompareh <- prepCompare(dfPVAC, "PVAC")

#Add Cost data 
dfCompare <- merge(dfCompare, costs[1:6], by.x="t", by.y = "Year")
dfCompareh <- merge(dfCompareh, costsh[1:6], by.x="t", by.y = "Year")

#Add Cost Data for HT&T and Combos w/ HT&T
#costs_test * tot_pop + costs_Tae*tae_cases+ costs_Cyst*cysti_cases)
dfCompare <- dfCompare %>% mutate(HTT_Cost = costs_test*tot_pop*.8 + 
                         cost_tae*dfCompare$HTT_H_Tae +
                         cost_cysti*dfCompare$HTT_H_Cysti)
dfCompareh <- dfCompareh %>% mutate(HTT_Cost = costs_test*tot_pop + 
                         cost_tae*dfCompareh$HTT_H_Tae +
                         cost_cysti*dfCompareh$HTT_H_Cysti)

#Export Cost info in nice graphic
dfCostDisplay <- dfCompare[, endsWith(colnames(dfCompare), "_Cost")]
dfCostDisplay <- select(dfCostDisplay,1:5)
dfCostDisplay$t <- 1:30
dfCostDisplay <- dfCostDisplay[, c(6,1,2,3, 4, 5)]
dfCostDisplay[,1] <-formatC(dfCostDisplay[,1], format="d", big.mark = ",")
#for(i in 1:nrow(dfCostDisplay)){
#  dfCostDisplay[,i] <-formatC(dfCostDisplay[,i], format="d", big.mark = ",")
#}
colnames(dfCostDisplay) = c("Years", "Status Quo", "Sanitation", "Pig MDA","Pig Vaccination", "Human T&T")

cTbl <- dfCostDisplay[1:22,] %>%
  kbl(caption = "Costs (USD) per Year by Intervention ", longtable = T, ) %>%
  kable_classic(full_width = F, html_font = "Cambria")


dfCostDisplayh <- dfCompareh[, endsWith(colnames(dfCompareh), "_Cost")]
dfCostDisplayh <- select(dfCostDisplayh,1:5)
dfCostDisplayh$t <- 1:30
dfCostDisplayh <- dfCostDisplayh[, c(6,1,2,3, 4, 5)]
dfCostDisplayh[,1] <-formatC(dfCostDisplayh[,1], format="d", big.mark = ",")
#for(i in 1:nrow(dfCostDisplayh)){
#  dfCostDisplayh[,i] <-formatC(dfCostDisplayh[,i], format="d", big.mark = ",")
#}
colnames(dfCostDisplayh) = c("Years", "Status Quo", "Sanitation", "Pig MDA","Pig Vaccination", "Human T&T")

cTblh <- dfCostDisplayh[1:22,] %>%
  kbl(caption = "Costs (USD) per Year by Intervention ", longtable = T, ) %>%
  kable_classic(full_width = F, html_font = "Cambria")

#Copy values to google drive
#library("writexl")
#xlsD <- select(dfCompare, HTT_Cost)
#write_xlsx(xlsD,"xlsD.xlsx")

#Run BCR Calculations
#calcBCR(dfCompare, "SAN")

```


```{r}
#Calculate # of human cases averted by the intervention
dfCompare <- dfCompare %>% 
  mutate(bcr_PMDA = ((SQ_P_Cysti-PMDA_P_Cysti)*costPig + (SQ_H_Cysti - PMDA_H_Cysti)*costHuman) / PMDA_Cost) %>% 
  mutate(bcr_SAN = ((SQ_P_Cysti-SAN_P_Cysti)*costPig + (SQ_H_Cysti - SAN_H_Cysti)*costHuman) / SAN_Cost) %>% 
  mutate(bcr_PVAC = ((SQ_P_Cysti-PVAC_P_Cysti)*costPig + (SQ_H_Cysti - PVAC_H_Cysti)*costHuman) / PVAC_Cost) %>%
  mutate(bcr_HTT = ((SQ_P_Cysti-HTT_P_Cysti)*costPig + (SQ_H_Cysti - HTT_H_Cysti)*costHuman) / HTT_Cost)

```

## Cost Effectiveness Analysis How much does it cost to avert each DALY

* The total number of DALYs in Burkina Faso in 2019 was 2064 (IHME).

```{r}
#Estimated DALYS per Human Cysticercosis case
#20.3 million people in BF; 4.5% of population with active cases; 2,064 DALYS

dalysPerCase <- 2064 / (0.045 * tot_pop)

#Calculate how many DALYS were averted each year
dfCompare <- dfCompare %>% 
  mutate(SAN_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - SAN_H_Cysti)) %>% 
  mutate(PMDA_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - PMDA_H_Cysti)) %>% 
  mutate(PVAC_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - PVAC_H_Cysti)) %>% 
  mutate(HTT_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - HTT_H_Cysti)) 

#Cumulative DALYS averted
dfCompare$SAN_CUM_DALYS_Avert <- dfCompare$SAN_DALYS_Avert
dfCompare$PMDA_CUM_DALYS_Avert <- dfCompare$PMDA_DALYS_Avert
dfCompare$PVAC_CUM_DALYS_Avert <- dfCompare$PVAC_DALYS_Avert
dfCompare$HTT_CUM_DALYS_Avert <- dfCompare$HTT_DALYS_Avert

for (row in 2:nrow(dfCompare)) {
    dfCompare[row, "SAN_CUM_DALYS_Avert"] <- dfCompare[row, "SAN_DALYS_Avert"] + dfCompare[row-1, "SAN_CUM_DALYS_Avert"]
    dfCompare[row, "PMDA_CUM_DALYS_Avert"] <- dfCompare[row, "PMDA_DALYS_Avert"] + dfCompare[row-1, "PMDA_CUM_DALYS_Avert"]
    dfCompare[row, "PVAC_CUM_DALYS_Avert"] <- dfCompare[row, "PVAC_DALYS_Avert"] + dfCompare[row-1, "PVAC_CUM_DALYS_Avert"]
    dfCompare[row, "HTT_CUM_DALYS_Avert"] <- dfCompare[row, "HTT_DALYS_Avert"] + dfCompare[row-1, "HTT_CUM_DALYS_Avert"]
}

#Calculate how much each DALY averted cost
dfCompare <- dfCompare %>% 
  mutate(SAN_Cost_DALY = SAN_Cost/SAN_DALYS_Avert) %>%
  mutate(PMDA_Cost_DALY = PMDA_Cost/PMDA_DALYS_Avert) %>%
  mutate(PVAC_Cost_DALY = PVAC_Cost/PVAC_DALYS_Avert) %>%
  mutate(HTT_Cost_DALY = HTT_Cost/HTT_DALYS_Avert)

##### Cumulative Costs per cumulative DALYs averted #####
dfCompare$SQ_CUM_Cost <- dfCompare$SQ_Cost
dfCompare$SAN_CUM_Cost <- dfCompare$SAN_Cost
dfCompare$PMDA_CUM_Cost <- dfCompare$PMDA_Cost
dfCompare$PVAC_CUM_Cost <- dfCompare$PVAC_Cost
dfCompare$HTT_CUM_Cost <- dfCompare$HTT_Cost

#higher parameters
dfCompareh$SQ_CUM_Cost <- dfCompareh$SQ_Cost
dfCompareh$SAN_CUM_Cost <- dfCompareh$SAN_Cost
dfCompareh$PMDA_CUM_Cost <- dfCompareh$PMDA_Cost
dfCompareh$PVAC_CUM_Cost <- dfCompareh$PVAC_Cost
dfCompareh$HTT_CUM_Cost <- dfCompareh$HTT_Cost


for (row in 2:nrow(dfCompare)) {
    dfCompare[row, "SQ_CUM_Cost"] <- dfCompare[row, "SQ_Cost"] + dfCompare[row-1, "SQ_CUM_Cost"]
    dfCompare[row, "SAN_CUM_Cost"] <- dfCompare[row, "SAN_Cost"] + dfCompare[row-1, "SAN_CUM_Cost"]
    dfCompare[row, "PMDA_CUM_Cost"] <- dfCompare[row, "PMDA_Cost"] + dfCompare[row-1, "PMDA_CUM_Cost"]
    dfCompare[row, "PVAC_CUM_Cost"] <- dfCompare[row, "PVAC_Cost"] + dfCompare[row-1, "PVAC_CUM_Cost"]
    dfCompare[row, "HTT_CUM_Cost"] <- dfCompare[row, "HTT_Cost"] + dfCompare[row-1, "HTT_CUM_Cost"]
}

for (row in 2:nrow(dfCompareh)) {
    dfCompareh[row, "SQ_CUM_Cost"] <- dfCompareh[row, "SQ_Cost"] + dfCompareh[row-1, "SQ_CUM_Cost"]
    dfCompareh[row, "SAN_CUM_Cost"] <- dfCompareh[row, "SAN_Cost"] + dfCompareh[row-1, "SAN_CUM_Cost"]
    dfCompareh[row, "PMDA_CUM_Cost"] <- dfCompareh[row, "PMDA_Cost"] + dfCompareh[row-1, "PMDA_CUM_Cost"]
    dfCompareh[row, "PVAC_CUM_Cost"] <- dfCompareh[row, "PVAC_Cost"] + dfCompareh[row-1, "PVAC_CUM_Cost"]
    dfCompareh[row, "HTT_CUM_Cost"] <- dfCompareh[row, "HTT_Cost"] + dfCompareh[row-1, "HTT_CUM_Cost"]
}


```

## After 10 years, cumulative cost effectiveness analysis

```{r, message=FALSE, warning=FALSE}
library("data.table")
library("hesim")
library("magrittr") 

n_samples = 1000
set.seed(212)
#cost
cost <- vector(mode = "list", length = 5)
names(cost) <- c("Status Quo", "Pig MDA", "Pig Vaccine", "HT&T", "Sanitation")
cost[[1]] <- runif(n_samples, dfCompare[10, "SQ_CUM_Cost"],dfCompareh[10, "SQ_CUM_Cost"])
cost[[2]] <- runif(n_samples, dfCompare[10, "PMDA_CUM_Cost"],dfCompareh[10, "PMDA_CUM_Cost"])
cost[[3]] <- runif(n_samples, dfCompare[10, "PVAC_CUM_Cost"],dfCompareh[10, "PVAC_CUM_Cost"])
cost[[4]] <- runif(n_samples, dfCompare[10, "HTT_CUM_Cost"],dfCompareh[10, "HTT_CUM_Cost"])
cost[[5]] <- runif(n_samples, dfCompare[10, "SAN_CUM_Cost"],dfCompareh[10, "SAN_CUM_Cost"])

# effectiveness
daly <- cost
#rnorm(n, mean = 0, sd = 1)
daly[[1]] <- runif(n_samples, 1,1)
daly[[2]] <- runif(n_samples, dfCompare[10, "PMDA_CUM_DALYS_Avert"],dfCompare[10, "PMDA_CUM_DALYS_Avert"])
daly[[3]] <- runif(n_samples, dfCompare[10, "PVAC_CUM_DALYS_Avert"],dfCompare[10, "PVAC_CUM_DALYS_Avert"])
daly[[4]] <- runif(n_samples, dfCompare[10, "HTT_CUM_DALYS_Avert"],dfCompare[10, "HTT_CUM_DALYS_Avert"])
daly[[5]] <- runif(n_samples, dfCompare[10, "SAN_CUM_DALYS_Avert"],dfCompare[10, "SAN_CUM_DALYS_Avert"])

ce <- data.table(sample = rep(seq(n_samples), length(daly)),
                 strategy = rep(paste0("Strategy ", seq(1, 5)), 
                                each = n_samples),
                 cost = do.call("c", cost), qalys = do.call("c", daly))

ce <- ce %>% mutate(strategy = 
                      case_when(strategy == "Strategy 1" ~ "Status Quo",
                              strategy == "Strategy 2" ~ "Pig MDA",
                              strategy == "Strategy 3" ~ "Pig Vaccine",
                              strategy == "Strategy 4" ~ "HT&T",
                              strategy == "Strategy 5" ~ "Sanitation"))

colnames(ce)[4]<-"dalys"
ceTb <- ce[1995:2010,] %>%
  kbl(caption = "Simulations with Range of Cost Parameters", longtable = T, ) %>%
  kable_classic(full_width = F, html_font = "Cambria") 

#tapply(ce$cost, ce$strategy, summary)

ce_easy <- ce %>% mutate(cost = cost/1000000)
colnames(ce_easy)[3]<- "cost_106"

#plot to see data
ggplot(data=ce_easy, aes(x=as.factor(strategy), y=cost_106)) +
  geom_boxplot()

#Willingness to pay
ktop <- 1000000
ktop2 <-100
cea_out <-  cea(ce, k = seq(0, ktop, 10000), 
                sample = "sample", strategy = "strategy", 
                e = "dalys", c = "cost")

#Graph of Willingness to Pay
plot_ceac(cea_out) + geom_jitter()+theme_light()+xlab("Willingness to Pay Per DALY Averted")

cea_out$summary
cea_pw_out <-  cea_pw(ce_easy,  k = seq(0, ktop2, 1), 
                      comparator = "Status Quo",
                      sample = "sample", strategy = "strategy",
                      e = "dalys", c = "cost_106")
cea_pw_out$summary[,3:8] <- round(cea_pw_out$summary[,3:8],0)
cea_pw_out$summary
ceaTbl <- icer(cea_pw_out, k = 100) %>% format()
ceaTbl[1,1] <- c("Incremental DALY Averted")

View(ceaTbl[-c(3),])
ceaTbl2 <- ceaTbl[-c(3),] %>%
  kbl(caption = "Incremental Cost-effectiveness Ratio (ICER) Compared to Status Quo after 10 Years", longtable = T) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  footnote("Costs in Millions USD")
print(ceaTbl2)

```

