---
title: "Burkina Faso data using EpiCyst Model"
date: "27.04.2021"
---
```{r, include=FALSE}
rm(list = ls())
Sys.setenv(LANG = "en")
setwd("C:/Users/morika/Desktop/AdvOneHealth/")

library(epicyst)
library(ggplot2)
library(dampack)
library(kableExtra)
library(dplyr)
library(googlesheets4)
```

```{r eval=FALSE, include=FALSE}
url <- "https://docs.google.com/spreadsheets/d/1XuV9UIDp1d1u3_KCbZgHSKUpXTbuXDoSRjNfMxfzgO4/edit#gid=1862836567"
read_sheet(url)
ssid <- as_sheets_id(url)
unclass(ssid)
#gs_auth(new_user = TRUE)
```
## Import Data from Google Sheets

```{r, message=FALSE, warning=FALSE}

gs4_auth(
email = "kathleenbmoriarty@gmail.com",
path = NULL,
scopes = "https://www.googleapis.com/auth/drive",
cache = "path_to_cache",
use_oob = FALSE,
token = NULL)

ssid <- "1XuV9UIDp1d1u3_KCbZgHSKUpXTbuXDoSRjNfMxfzgO4"
costs <- read_sheet(ssid, sheet = "SSA_Costs_V2")
#dalys <- read_sheet(ssid, sheet = "SSA_DALYs", range = "A2:B7")
cparams <- read_sheet(ssid, sheet = "BF_Params")

```

## Initial setup

```{r}

#Create Burkina Faso subset
aparams <- set_up(PPS=cparams[which(cparams$Param=="PPS"),]$Val, 
                   HPS = cparams[which(cparams$Param=="HPS"),]$Val,
                   TPrev = cparams[which(cparams$Param=="TPrev"),]$Val, 
                   CPrev = cparams[which(cparams$Param=="CPrev"),]$Val, 
                   LEH=cparams[which(cparams$Param=="LEH"),]$Val, 
                   LEP=cparams[which(cparams$Param=="LEP"),]$Val)

#Parameters
#aparams[[1]]$HPS

#State variables
#aparams[[2]]

```

## Run model with Baseline and Interventions
* time: months
* steps: per unit of time


```{r}

dfSQ <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1)

g1 <- ggplot(data=dfSQ, aes(x=t/12, y=Humans_Cysticercosis/1000, color="Baseline"))+
  geom_line()+
  ylim(0,1000)+ 
  xlim(0,30)+
  labs(title="T. Solium Interventions in Burkina Faso",x="Time (years)", y = "Human Cysticercosis Cases (x 10^3)") +
  theme_light() +
  theme(legend.title = element_blank()) 

#Model with Sanitation intervention
dfSAN <- run_model(params=aparams[[1]], initial_states=aparams[[2]], time = 50, step = 1, intervention="Sanitation", intervention_time = 3)

#Model with Pig MDA intervention
dfPMDA <- run_model(params=aparams[[1]], initial_states=aparams[[2]], time = 50, step = 1, intervention="Pig_MDA", intervention_time = 3)

#Model with Pig Vaccination intervention
dfPVAC <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention="Pig_vaccine", intervention_time = 3)

#Model with HT&T intervention
#Updated effect_size of HT&T to assume coverage of 80% instead of 90%
#assumed therapeutic coverage (80%) × sensitivity of test to T. solium (0.97) × specificity of the test to cysticercosis infection (0.98) × assumed drug efficacy (99%) = 0.75
eff <- intervention_effect_size()
eff$Human_test_and_treat <- 0.75
dfHTT <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention="Human_test_and_treat", intervention_time = 3, intervention_effect = eff)

#Model with Pig MDA + Pig Vaccination intervention
dfPCOMBO <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention=c("Pig_MDA","Pig_vaccine"), intervention_time = 3)

#Model with Pig MDA + Pig Vaccination + HT&T intervention
dfACOMBO <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention=c("Pig_MDA","Pig_vaccine", "Human_test_and_treat"), intervention_time = 3, intervention_effect = eff)

#Model with Pig MDA + Sanitation
dfPSCOMBO <- run_model(params=aparams[[1]], initial_states =aparams[[2]], time = 50, step = 1, intervention=c("Pig_MDA","Sanitation"), intervention_time = 3)

#Add to graph
g2<- g1 + 
  geom_line(data=dfSAN, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Sanitation")) +
  geom_line(data=dfPMDA, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA")) +
  geom_line(data=dfPVAC, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig Vaccination")) +
  geom_line(data=dfHTT, aes(x=t/12,y=Humans_Cysticercosis/1000, color="HT&T")) +
  geom_line(data=dfPCOMBO, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA + Pig Vaccination"))+
  geom_line(data=dfACOMBO, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA + Pig Vacc + HT&T")) +
  geom_line(data=dfPSCOMBO, aes(x=t/12,y=Humans_Cysticercosis/1000, color="Pig MDA + Sanitation"))
  

#Changing graph features 
g2 <- g2 + scale_colour_manual("", 
                      breaks = c("Baseline","Sanitation","Pig MDA", 
                                 "Pig Vaccination", "HT&T", "Pig MDA + Pig Vaccination", 
                                 "Pig MDA + Pig Vacc + HT&T", "Pig MDA + Sanitation"),
                      values = c("black", "purple", "blue","green","darkorange2","deeppink1","turquoise3", "slategrey")) +
  theme_light() +
  theme(legend.title = element_blank()) 

plot(g2)


```


## Calculate R0

```{r}
r0(params= aparams[[1]])

```

## BCR: Benefit Cost Ratio

### Assumptions:

* Cost per pig case of cysti: 14 USD
* Cost per human case of cysti: 230 USD
* Other costs explained in spreadsheets

```{r}
#Intial values
costPig <- as.double(costs[1,"Cost_Per_Pig_Case"])
costHuman <- as.double(costs[1,"Cost_Per_Human_Case"])

tot_pop = aparams[[1]]$HPS
cost_tae = as.double(costs[1,"Costs_HTT_Taeniasis"])
cost_cysti = as.double(costs[1,"Costs_HTT_Cysti"])
costs_test = as.double(costs[1,"Costs_HTT_Test"])


dfCompare <- data.frame(t=integer())

prepCompare = function(df, strAcronym) {

df_short <- df[which(df$t %% 12==1 & df$t < 362),]
df_short <- df_short %>%
  mutate(t = (t-1)/12) %>% 
  select(t, Humans_Cysticercosis, Pigs_Cysticercosis, Humans_Taeniasis)

#df_short <- df_short %>% select(t, Humans_Cysticercosis, Pigs_Cysticercosis, Humans_Taeniasis)
colnames(df_short) <- c("t", paste(strAcronym,"_H_Cysti", sep=""), paste(strAcronym,"_P_Cysti", sep=""), paste(strAcronym,"_H_Tae", sep=""))

#if dfCompare is empty, then set first intervention to equal dfCompare
if (dim(dfCompare)[1] == 0) {
  print("DFCOMPARE is empty")
  dfCompare <- df_short
} else {
  print("DFCOMPARE is nOT empty")
  
   dfCompare <- merge(dfCompare, df_short, by=c("t"))
}

  return(dfCompare)
}

#calcBCR = function(dfCompare, strAcronym){
#  bcr_tmp = paste("bcr_", strAcronym, sep="")
#  p_cysti_tmp = paste(strAcronym, "_P_Cysti", sep="")
#  h_cysti_tmp = paste(strAcronym, "_H_Cysti", sep="")
#  cost_tmp = paste(strAcronym, "_Cost", sep="")
#  
#  dfCompare <- dfCompare %>% mutate(bcr_tmp = ((SQ_P_Cysti-p_cysti_tmp)*costPig + #(SQ_H_Cysti-h_cysti_tmp)*costHuman) / cost_tmp)
#  
#  return(dfCompare)
#}

#Gather all data from the various model runs
dfCompare <- prepCompare(dfSQ, "SQ")
dfCompare <- prepCompare(dfSAN, "SAN")
dfCompare <- prepCompare(dfHTT, "HTT")
dfCompare <- prepCompare(dfPMDA, "PMDA")
dfCompare <- prepCompare(dfPVAC, "PVAC")
dfCompare <- prepCompare(dfACOMBO, "ACOMBO")
dfCompare <- prepCompare(dfPCOMBO, "PCOMBO")
dfCompare <- prepCompare(dfPSCOMBO, "PSCOMBO")

#Add Cost data 
dfCompare <- merge(dfCompare, costs[1:7], by.x="t", by.y = "Year")

#Add Cost Data for HT&T and Combos w/ HT&T
#costs_test * tot_pop + costs_Tae*tae_cases+ costs_Cyst*cysti_cases)
dfCompare <- dfCompare %>% mutate(HTT_Cost = costs_test*tot_pop + 
                         cost_tae*dfCompare$HTT_H_Tae +
                         cost_cysti*dfCompare$HTT_H_Cysti)
dfCompare <- dfCompare %>% mutate(ACOMBO_Cost = HTT_Cost + PCOMBO_Cost) 

#Export Cost info in nice graphic
View(dfCostDisplay)
dfCostDisplay <- dfCompare[, endsWith(colnames(dfCompare), "_Cost")]
dfCostDisplay <- select(dfCostDisplay,1:8)
dfCostDisplay$t <- 1:30
dfCostDisplay <- dfCostDisplay[, c(9,1,2,3, 5, 7, 6,4,8)]
dfCostDisplay[,1] <-formatC(dfCostDisplay[,1], format="d", big.mark = ",")
#for(i in 1:nrow(dfCostDisplay)){
#  dfCostDisplay[,i] <-formatC(dfCostDisplay[,i], format="d", big.mark = ",")
#}
colnames(dfCostDisplay) = c("Years", "Status Quo", "Sanitation", "Pig MDA","Pig Vaccination", "Human T&T", "Pig Combo","Pig MDA + Sanitation", "Pig Combo + Human T&T")

cTbl <- dfCostDisplay[1:22,] %>%
  kbl(caption = "Costs (USD) per Year by Intervention ", longtable = T, ) %>%
  kable_classic(full_width = F, html_font = "Cambria")

print(cTbl)
?kable_classic

#Copy values to google drive
#library("writexl")
#xlsD <- select(dfCompare, HTT_Cost)
#write_xlsx(xlsD,"xlsD.xlsx")

#Run BCR Calculations
#calcBCR(dfCompare, "SAN")

```


```{r}
### Transform time of prevalence dataframes ###

#Calculate # of human cases averted by the intervention
dfCompare <- dfCompare %>% 
  mutate(bcr_PMDA = ((SQ_P_Cysti-PMDA_P_Cysti)*costPig + (SQ_H_Cysti - PMDA_H_Cysti)*costHuman) / PMDA_Cost) %>% 
  mutate(bcr_SAN = ((SQ_P_Cysti-SAN_P_Cysti)*costPig + (SQ_H_Cysti - SAN_H_Cysti)*costHuman) / SAN_Cost) %>% 
  mutate(bcr_PVAC = ((SQ_P_Cysti-PVAC_P_Cysti)*costPig + (SQ_H_Cysti - PVAC_H_Cysti)*costHuman) / PVAC_Cost) %>%
  mutate(bcr_HTT = ((SQ_P_Cysti-HTT_P_Cysti)*costPig + (SQ_H_Cysti - HTT_H_Cysti)*costHuman) / HTT_Cost) %>%
  mutate(bcr_PCOMBO = ((SQ_P_Cysti-PCOMBO_P_Cysti)*costPig + (SQ_H_Cysti - PCOMBO_H_Cysti)*costHuman) / PCOMBO_Cost) %>%
  mutate(bcr_ACOMBO = ((SQ_P_Cysti-ACOMBO_P_Cysti)*costPig + (SQ_H_Cysti - ACOMBO_H_Cysti)*costHuman) / ACOMBO_Cost) %>%
  mutate(bcr_PSCOMBO = ((SQ_P_Cysti-PSCOMBO_P_Cysti)*costPig + (SQ_H_Cysti - PSCOMBO_H_Cysti)*costHuman) / PSCOMBO_Cost)

#Graph
c1 <- ggplot(dfCompare, aes(x=t, y=bcr_PMDA, color="Pig MDA")) +
  geom_line(size =1)+
  geom_line(aes(x=t, y=bcr_SAN, color="Sanitation"), size =1) +
  geom_line(aes(x=t, y=bcr_PVAC, color="Pig Vaccination"), size =1) +
  geom_line(aes(x=t, y=bcr_HTT, color="HT&T"), size =1) +
  geom_line(aes(x=t, y=bcr_PCOMBO, color="Pig Vaccine + Pig MDA"), size =1) +
  geom_line(aes(x=t, y=bcr_PSCOMBO, color="Pig MDA + Sanitation"), size =1) +
  geom_line(aes(x=t, y=bcr_ACOMBO, color="Pig Vaccine + Pig MDA + HT&T"), size =1) +
  labs(title="Benefit Cost Ratio", x="Time (years)", y="Costs Averted / Intervention Cost") +
  theme_light() +
  theme(legend.title = element_blank()) 

plot(c1)

View(dfCompare)
```

## Cost Effectiveness Analysis How much does it cost to avert each DALY

* The total number of DALYs in Burkina Faso in 2019 was 2064 (IHME).

```{r}
#Estimated DALYS per Human Cysticercosis case
#20.3 million people in BF; 4.5% of population with active cases; 2,064 DALYS

dalysPerCase <- 2064 / (0.045 * tot_pop)

#Calculate how many DALYS were averted each year
dfCompare <- dfCompare %>% 
  mutate(SAN_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - SAN_H_Cysti)) %>% 
  mutate(PMDA_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - PMDA_H_Cysti)) %>% 
  mutate(PVAC_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - PVAC_H_Cysti)) %>% 
  mutate(HTT_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - HTT_H_Cysti)) %>% 
  mutate(PCOMBO_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - PCOMBO_H_Cysti)) %>% 
  mutate(PSCOMBO_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - PSCOMBO_H_Cysti)) %>% 
  mutate(ACOMBO_DALYS_Avert = dalysPerCase*(SQ_H_Cysti - ACOMBO_H_Cysti))
 
#Cumulative DALYS averted
dfCompare$SAN_CUM_DALYS_Avert <- dfCompare$SAN_DALYS_Avert
dfCompare$PMDA_CUM_DALYS_Avert <- dfCompare$PMDA_DALYS_Avert
dfCompare$PVAC_CUM_DALYS_Avert <- dfCompare$PVAC_DALYS_Avert
dfCompare$HTT_CUM_DALYS_Avert <- dfCompare$HTT_DALYS_Avert
dfCompare$PCOMBO_CUM_DALYS_Avert <- dfCompare$PCOMBO_DALYS_Avert
dfCompare$PSCOMBO_CUM_DALYS_Avert <- dfCompare$PSCOMBO_DALYS_Avert
dfCompare$ACOMBO_CUM_DALYS_Avert <- dfCompare$ACOMBO_DALYS_Avert

for (row in 2:nrow(dfCompare)) {
    dfCompare[row, "SAN_CUM_DALYS_Avert"] <- dfCompare[row, "SAN_DALYS_Avert"] + dfCompare[row-1, "SAN_CUM_DALYS_Avert"]
    dfCompare[row, "PMDA_CUM_DALYS_Avert"] <- dfCompare[row, "PMDA_DALYS_Avert"] + dfCompare[row-1, "PMDA_CUM_DALYS_Avert"]
    dfCompare[row, "PVAC_CUM_DALYS_Avert"] <- dfCompare[row, "PVAC_DALYS_Avert"] + dfCompare[row-1, "PVAC_CUM_DALYS_Avert"]
    dfCompare[row, "HTT_CUM_DALYS_Avert"] <- dfCompare[row, "HTT_DALYS_Avert"] + dfCompare[row-1, "HTT_CUM_DALYS_Avert"]
    dfCompare[row, "PCOMBO_CUM_DALYS_Avert"] <- dfCompare[row, "PCOMBO_DALYS_Avert"] + dfCompare[row-1, "PCOMBO_CUM_DALYS_Avert"]
    dfCompare[row, "PSCOMBO_CUM_DALYS_Avert"] <- dfCompare[row, "PSCOMBO_DALYS_Avert"] + dfCompare[row-1, "PSCOMBO_CUM_DALYS_Avert"]
    dfCompare[row, "ACOMBO_CUM_DALYS_Avert"] <- dfCompare[row, "ACOMBO_DALYS_Avert"] + dfCompare[row-1, "ACOMBO_CUM_DALYS_Avert"]
}

c2 <- ggplot(dfCompare, aes(x=t, y=SAN_CUM_DALYS_Avert, color="Sanitation"))+
  geom_line(size=1)+
  geom_line(aes(x=t, y=PMDA_CUM_DALYS_Avert, color="Pig MDA"), size=1) +
  geom_line(aes(x=t, y=PVAC_CUM_DALYS_Avert, color="Pig Vaccination"), size=1) +
  geom_line(aes(x=t, y=HTT_CUM_DALYS_Avert, color="HT&T"), size=1) +
  geom_line(aes(x=t, y=PCOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA"), size=1) +
  geom_line(aes(x=t, y=ACOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA + HT&T"), size=1) +
  geom_line(aes(x=t, y=PSCOMBO_CUM_DALYS_Avert, color="Pig MDA + Sanitation"), size=1, position=position_jitter(w=0.02, h=0)) +
  labs(title="Cumulative DALYS Averted by Intervention per Year", x="Time (years)", 
       y="Cumulative DALYS Averted") +
  theme_light() +
  theme(legend.title = element_blank()) 

plot(c2)

View(dfCompare$PSCOMBO_CUM_DALYS_Avert)

#Calculate how much each DALY averted cost
dfCompare <- dfCompare %>% 
  mutate(SAN_Cost_DALY = SAN_Cost/SAN_DALYS_Avert) %>%
  mutate(PMDA_Cost_DALY = PMDA_Cost/PMDA_DALYS_Avert) %>%
  mutate(PVAC_Cost_DALY = PVAC_Cost/PVAC_DALYS_Avert) %>%
  mutate(HTT_Cost_DALY = HTT_Cost/HTT_DALYS_Avert) %>%
  mutate(PCOMBO_Cost_DALY = PCOMBO_Cost/PCOMBO_DALYS_Avert) %>%
  mutate(PSCOMBO_Cost_DALY = PSCOMBO_Cost/PSCOMBO_DALYS_Avert) %>%
  mutate(ACOMBO_Cost_DALY = ACOMBO_Cost/ACOMBO_DALYS_Avert)

c3 <- ggplot(dfCompare, aes(x=t, y=SAN_Cost_DALY, color="Sanitation"))+
  geom_line()+
  geom_line(aes(x=t, y=PMDA_Cost_DALY, color="Pig MDA")) +
  geom_line(aes(x=t, y=PVAC_Cost_DALY, color="Pig Vaccination")) +
  geom_line(aes(x=t, y=HTT_Cost_DALY, color="HT&T")) +
  geom_line(aes(x=t, y=PCOMBO_Cost_DALY, color="Pig Vaccine + Pig MDA")) +
  geom_line(aes(x=t, y=PSCOMBO_Cost_DALY, color="Pig MDA + Sanitation")) +
  geom_line(aes(x=t, y=ACOMBO_Cost_DALY, color="Pig Vaccine + Pig MDA + HT&T")) +
  labs(title="Intervention Cost per DALY", x="Time (years)", y="Cost (USD) per DALY") +
  theme_light() +
  theme(legend.title = element_blank()) 

plot(c3)

#Cumulative Costs per cumulative DALYs averted 
dfCompare$SAN_CUM_Cost <- dfCompare$SAN_Cost
dfCompare$PMDA_CUM_Cost <- dfCompare$PMDA_Cost
dfCompare$PVAC_CUM_Cost <- dfCompare$PVAC_Cost
dfCompare$HTT_CUM_Cost <- dfCompare$HTT_Cost
dfCompare$PCOMBO_CUM_Cost <- dfCompare$PCOMBO_Cost
dfCompare$PSCOMBO_CUM_Cost <- dfCompare$PSCOMBO_Cost
dfCompare$ACOMBO_CUM_Cost <- dfCompare$ACOMBO_Cost

for (row in 2:nrow(dfCompare)) {
    dfCompare[row, "SAN_CUM_Cost"] <- dfCompare[row, "SAN_Cost"] + dfCompare[row-1, "SAN_CUM_Cost"]
    dfCompare[row, "PMDA_CUM_Cost"] <- dfCompare[row, "PMDA_Cost"] + dfCompare[row-1, "PMDA_CUM_Cost"]
    dfCompare[row, "PVAC_CUM_Cost"] <- dfCompare[row, "PVAC_Cost"] + dfCompare[row-1, "PVAC_CUM_Cost"]
    dfCompare[row, "HTT_CUM_Cost"] <- dfCompare[row, "HTT_Cost"] + dfCompare[row-1, "HTT_CUM_Cost"]
    dfCompare[row, "PCOMBO_CUM_Cost"] <- dfCompare[row, "PCOMBO_Cost"] + dfCompare[row-1, "PCOMBO_CUM_Cost"]
    dfCompare[row, "PSCOMBO_CUM_Cost"] <- dfCompare[row, "PSCOMBO_Cost"] + dfCompare[row-1, "PSCOMBO_CUM_Cost"]
    dfCompare[row, "ACOMBO_CUM_Cost"] <- dfCompare[row, "ACOMBO_Cost"] + dfCompare[row-1, "ACOMBO_CUM_Cost"]
}

c4 <- ggplot(dfCompare, aes(x=t, y=SAN_CUM_Cost/SAN_CUM_DALYS_Avert, color="Sanitation"))+
  geom_line(size=1)+
  geom_line(aes(x=t, y=PMDA_CUM_Cost/PMDA_CUM_DALYS_Avert, color="Pig MDA"), size=1) +
  geom_line(aes(x=t, y=PVAC_CUM_Cost/PVAC_CUM_DALYS_Avert, color="Pig Vaccination"),size=1) +
  geom_line(aes(x=t, y=HTT_CUM_Cost/HTT_CUM_DALYS_Avert, color="HT&T"), size=1) +
  geom_line(aes(x=t, y=PCOMBO_CUM_Cost/PCOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA"), size=1) +
  geom_line(aes(x=t, y=PSCOMBO_CUM_Cost/PSCOMBO_CUM_DALYS_Avert, color="Pig MDA + Sanitation"), size=1) +
  geom_line(aes(x=t, y=ACOMBO_CUM_Cost/ACOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA + HT&T"), size=1) +
  labs(x="Time (years)", y="Cumulative Cost (USD) per Cumulative DALY") +
  theme_light() +
  theme(legend.title = element_blank())+
  ylim(0,1000000)+
  xlim(4,30)

c4.1 <- ggplot(dfCompare, aes(x=t, y=SAN_CUM_Cost/SAN_CUM_DALYS_Avert, color="Sanitation"))+
  geom_line(size=1)+
  geom_line(aes(x=t, y=PMDA_CUM_Cost/PMDA_CUM_DALYS_Avert, color="Pig MDA"),size=1) +
  geom_line(aes(x=t, y=PVAC_CUM_Cost/PVAC_CUM_DALYS_Avert, color="Pig Vaccination"),size=1) +
  geom_line(aes(x=t, y=HTT_CUM_Cost/HTT_CUM_DALYS_Avert, color="HT&T"),size=1) +
  geom_line(aes(x=t, y=PCOMBO_CUM_Cost/PCOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA"),size=1) +
  geom_line(aes(x=t, y=PSCOMBO_CUM_Cost/PSCOMBO_CUM_DALYS_Avert, color="Pig MDA + Sanitation"),size=1) +
  geom_line(aes(x=t, y=ACOMBO_CUM_Cost/ACOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA + HT&T"),size=1) +
  labs(x="Time (years)", y="Cumulative Cost (USD) per Cumulative DALY") +
  theme_light() +
  theme(legend.title = element_blank())+
  ylim(0,100000)+
  xlim(10,30)

c4.2 <- ggplot(dfCompare, aes(x=t, y=SAN_CUM_Cost/SAN_CUM_DALYS_Avert, color="Sanitation"))+
  geom_line(size=1)+
  geom_line(aes(x=t, y=PMDA_CUM_Cost/PMDA_CUM_DALYS_Avert, color="Pig MDA"),size=1) +
  geom_line(aes(x=t, y=PVAC_CUM_Cost/PVAC_CUM_DALYS_Avert, color="Pig Vaccination"),size=1) +
  geom_line(aes(x=t, y=HTT_CUM_Cost/HTT_CUM_DALYS_Avert, color="HT&T"),size=1) +
  geom_line(aes(x=t, y=PCOMBO_CUM_Cost/PCOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA"),size=1) +
  geom_line(aes(x=t, y=PSCOMBO_CUM_Cost/PSCOMBO_CUM_DALYS_Avert, color="Pig MDA + Sanitation"),size=1) +
  geom_line(aes(x=t, y=ACOMBO_CUM_Cost/ACOMBO_CUM_DALYS_Avert, color="Pig Vaccine + Pig MDA + HT&T"),size=1) +
  labs(x="Time (years)", y="Cumulative Cost (USD) per Cumulative DALY") +
  theme_light() +
  theme(legend.title = element_blank())+
  ylim(0,10000)+
  xlim(10,30)

plot(c4)
plot(c4.1)
plot(c4.2)


```
